\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-13 NAR_DRAFT.tex
another paragraph

We have chosen to implement \batcave as a post-calling algorithm for use with MuTect because it presents a simple model and a well-tested set of heuristic filters.
However, in principle there is no barrier to using the method with other variant callers.
For instance Strelka, another widely used variant caller, computes a joint posterior probability over tumor and normal genotypes where the prior probability of that the tumor carries a somatic mutation is set to a constant.
Modifying the algorithm to work with the Strelka statistical model would involve replacing the constant prior with a tumor and site-specific prior for each potential variant, exactly as we have done with MuTect.
In general we are advancing the idea that there is substantial prior information about the site-specific mutation probability encoded in NGS data, and we should be using it.

>>>>

We have chosen to implement \batcave as a post-calling algorithm for use with MuTect because it presents a simple model and a well-tested set of heuristic filters.
However, in principle there is no barrier to using the method with other variant callers.
For instance Strelka2, another widely used variant caller, computes a joint posterior probability over tumor and normal genotypes where the prior probability that the tumor carries a somatic mutation at a given site is set to a constant \cite{Kim2018}.
Modifying the algorithm to work with the Strelka statistical model would involve replacing the constant prior with a tumor and site-specific prior for each potential variant, exactly as we have done with MuTect.
In general we are advancing the idea that there is substantial prior information about the tumor and site-specific mutation probability encoded in NGS data, and we should be using it.
